Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression

### 2019-04-21 index.Rmd
moved \usepackage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, tidy = TRUE, out.width = "90%", fig.align = "center", out.extra = "")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, tidy = TRUE, out.width = "85%", fig.align = "center", out.extra = "")

# load packages
library(magrittr)
library(dplyr)
library(ggplot2)
library(pander)
